Investigating the possible Factors affecting Canadian Individuals and Families' Feelings about Life

### 2022-03-21 output/paper3.Rmd
fix2

---
title: "Investigating the possible aspects affecting Canadian individuals and families' feelings about life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and more working hours feel happier about life, while married peole of older age with less working hours and higher educational level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---

>>>>

---
title: "Investigating the possible Factors affecting Canadian Individuals and Families' Feelings about Life"
author: 
  - Alicia Yang
  - Jiayi Du
  - Kaiyuan Yan
thanks: "Code and data are available at: https://github.com/dujiayi1/Factors-that-affect-happiness."
date: "`r format(Sys.time(), '%d %B %Y')`"
abstract: "In recent years Canadian society has shown diverse attitude towards the idea of forming a family. To investigate on the reason behind this controversy, this paper conducted the research on the factors which may have an impact on single and married people’s feelings about life based on the General Social Survey(GSS). After screening and comparison, we found that the factors that may affect people’s feelings about life in the survey include age, respondent income, sex, average working hours, and education level. By observing the result, we found that single people of younger age with less income and more working hours feel happier about life, while married peole of older age with less working hours and higher educational level feel more satisfied with their life. Moreover, we analyzed the reason for these factors causing effect and discussed the possible bias in the research and the solutions to it."
output:
  bookdown::pdf_document2
toc: FALSE
bibliography: references.bib
---
